%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Archit}{Jain}{ 
\urlstyle{same}\url{https://www.facebook.com/archit.jain.562} \\
\href{mailto:archit.dtu.jain@gmail.com}{archit.dtu.jain@gmail.com} | (+91)9582910353
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Delhi Technological}
\subsection{University}
\descript{B.Tech -Computer Science}
\location{Expected June 2017 | Delhi, India \\ Aggregate: 83.4\% *}
\sectionsep

\subsection{Sachdeva Public School}
\descript{All India Senior Secondary}
\descript{Certificate Examination}
\location{May 2013 | Aggregate: 96.4\% *}
\sectionsep

\descript{All India Secondary School}
\descript{Examination}
\location{May 2011 | CGPA: 9.6}
\sectionsep

\subsection{All India Engineering}
\subsection{Enterance Exam}
\location{Rank 2087/14 lakh}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/archit09jain}{\custombold{archit09jain}} \\
LinkedIn://  \href{https://www.linkedin.com/in/archit-jain-603972102}{\custombold{archit-jain-603972102}} \\
Codechef://  \href{https://www.codechef.com/users/archit_jain08}{\custombold{archit\_jain08}} \\
Spoj://  \href{http://www.spoj.com/users/emo8/}{\custombold{emo8}} \\
Codeforces://  \href{http://codeforces.com/profile/archit_jain08}{\custombold{archit\_jain08}}
Hackerrank://  \href{https://www.hackerrank.com/archit_dtu_jain}{\custombold{archit\_dtu\_jain}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Algorithm Design and Analysis \\
Data Structures \\
Operating System\\
Computer Networks \\
Object Oriented Programming\\
Discrete Mathematics
\sectionsep

\subsection{Online}
Git and Github - Udacity\\
Intro to Machine Learning}- Udacity\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
\location{Proficient:}
C++ \textbullet{}   C  \\
\location{Intermediate:}
Python \textbullet{} JAVA\textbullet{} HTML \textbullet{} CSS\\
\location{Prior Knowledge:}
Android \textbullet{} PHP \textbullet{} Javascript\textbullet{} SQL
\sectionsep

\subsection{Tools and Framework}
Git\textbullet{} Sckit-Learn(ML) \textbullet{} Netbeans Ide
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Taxi driver Passenger Seeking System - Oct/Nov 2015}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\location{\urlstyle{same}\url{https://github.com/A-And-A/TaxiPassengerSeekingStrategies}}
\begin{tightemize}
\item Unsupervised Machine Learning - KMeans Algorithm.
\item Recommends nearby location where driver may find a customer booking.
\item Tools/API : Java Netbeans IDE, Google Maps API, JSON Parser.
\end{tightemize}
\sectionsep

\runsubsection{Accelerometer - Gesture Recognition - JAN/FEB 2016}
\location{\urlstyle{same}\url{https://github.com/archit09jain/IOT-Project}}
\begin{tightemize}
\item Internet of things - Accelerometer data collected from android smart phones and watches is used to predict the gesture performed by the user in a 3d space.
\item Accuracy of approx 91\% with SVM - C = 100 and Gamma = 0.001
\item Controls desktop applications like VLC media player and 2048 game.
\item Languages/Libraries : Java - Android, Python Scikit-Learn, Sqlite3, numpy, matplotlib,pyuserinput - pykeyboard and pymouse.
.\end{tightemize}
\sectionsep

\subsection{Code and Share - JUN/JUL 2015}
\location{\urlstyle{same}\url{https://github.com/A-and-A/Code-n-Share}}
\begin{tightemize}
\item Text editor with code compilation and sharing functionality over a same network during competitive programming competitions.
\item Developed for University Hostel LAN as an offline substitute of ideone.com using socket programming and ProcessBuilder class.
\item Tools/API : Java Netbens IDE.
\end{tightemize}
\sectionsep

\subsection{SPAM FILTER - JUN/JUL 2015}
\location{\urlstyle{same}\url{https://github.com/archit09jain/Spam-Filter}}
\begin{tightemize}
\item  SVM ­ 97.9\% and G.N. Bayes ­ 92.2\%
\item Tools/API : Java Netbens IDE and Pyhton Sckikt Learn.
\end{tightemize}
\sectionsep

\subsection{ANDROID AND WINDOWS AI MOBILE GAMES - OCT/DEC 2013}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item RUBIX(Android) - 2 Dimensional Rubik's cube with next move predictor.
\item CROSSX(Windows) - Tic -Tac -Toe (Single Player Mode Included)
\end{tightemize}
\sectionsep


\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{ACHIEVEMENTS} 
\begin{tabular}{rll}
2015	     &  69/2281  & Snapdeal Programming Hackathon - Hackerrank\\
2015	     &  85/1312  & Adobe Programming Hackathon - Hackerrank\\
2015     & National Rank 80 & Chennai ICPC Preliminary Round  \\
2015     & National Rank 111 & ACM-ICPC-Amritapuri Multi-site Regionals\\
2015     & 1/500 & BITS Programming contest by IEEE DTU\\
2015     & 1/300 & Sudocode programming contest by CSI DTU\\
2015     & 6/211 & DTU Programming Mania sponsered by Coding Blocks\\
2015     & National rank 110 & IOPC - IIT KANPUR\\
2015     & Global Rank 59/6456 & Codechef OCT Long Challenge\\
2016	     &  Qualified Round2 & Facebook Hackercup\\
2016	     &  44/4897  & Codagon - Codenation Coding Competition - Hackerrank\\
\end{tabular}
\begin{tightemize}
\item Amongst High Rated Coders in India on Programming Sites such as Codechef,Codeforces, Spoj etc.
\item Among Top 70 coders in India (according to Codechef Long Challenge Ratings)
\end{tightemize}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
